Evaluating the Performance and Energy Efficiency of COSMO-ART, a Fully Online Coupled Model System with Numerical Weather Forecast and Chemical Transport Models

### 2014-04-08 paper_enahpc14/Sec1:COSMO-ART.tex
adjusts structure of the document

\subsection{Model description}
\label{subsec:1.1}
COSMO-ART  (ART  stands  for   Aerosols  and  Reactive  Trace  gases),
developed  at  KIT  Karlsruhe  \citep{Vogel-2009}, is  a  regional  to
continental scale model coupled  online to the COSMO numerical weather
prediction  (NWP) and  climate  model \citep{Baldauf-2011}.   Physical
processes  like  transport,  turbulent  diffusion,  and  dry  and  wet
deposition  are  treated  together  with  photochemistry  and  aerosol
dynamics  using the  modal approach.

@@

\subsection{Model setup}
\label{subsec:1.2}
Establishing effective energy performance benchmarking of a code under
intense development such as COSMO-ART is a challenging task because of
the  absolute necessity that  results must  be reproducible  within an
expected  variance for the  duration of  the Exa2Green  project. After
consultation  with  the  climate  community  to  properly  define  the
baseline,  it was  necessary to  find a  run-configuration  capable of
being recreated in all subsequent versions of the code.

Thus, we give here a brief  overview of the main features of the model
setup for  our benchmark's daily  runs.  Three-dimensional simulations
are  performed over  Europe  for April  13th,  which is  close to  the
equinox and thus  brings benefits of having approximately  half day of
night  and half  day  of  sun exposure,  therefore  ensuring a  proper
activation of the chemistry cycle. We consider daily 24-hour forecasts
without  any  previous spin-up  simulations.   The calculation  domain
corresponds to  the CORDEX-EU-44  domain and is  covered by a  grid of
$222\times   216$    points   with   a    horizontal   resolution   of
$0.22\,^{\circ}$,  i.e.  50  km in  both directions,  and  40 vertical
layers.   Boundary  and initial  conditions,  emmissions and  external
parameters  were obtained by  the INT2LM  pre-processing interpolation
tool, which  performed the usual interpolation from  coarse grid model
data, and  INT2LM\_trcr\_ART, which consists mostly  of the definition
of a large number of  tracers.  The meteorological initial and bounday
conditions are  obtained by  the the ECMWF  global spectral  model IFS
with an update  frequency of 3h.  Boundary data  for gas-phase species
are taken from IFS-MOZART  output at 6h temporal resolution.  Multiple
runs of COSMO-ART were  performed to illustrate the reproducibility of
the baseline, and quantify  the significant uncertainties in the power
measurement,   as   dictated   by   the  available   technology   (see
subsection~\ref{subsec:3.2}).   The run-configuration  incorporates 34
2-d and 45 3-d fields to be written out every hour and doesn't include
data assimilation methods.

>>>>

\subsection{Model Description}
\label{subsec:1.1}
COSMO-ART  (ART  stands  for   Aerosols  and  Reactive  Trace  gases),
developed  at  KIT  Karlsruhe  \citep{Vogel-2009}, is  a  regional  to
continental scale model coupled  online to the COSMO numerical weather
prediction (NWP) and climate model \citep{Baldauf-2011}. It allows the
online calculation of reactive  trace substances and their interaction
with  the atmosphere.   Physical processes  like  transport, turbulent
diffusion,  and  dry and  wet  deposition  are  treated together  with
photochemistry and aerosol dynamics using the modal approach.

@@

\subsection{Model Setup}
\label{subsec:1.2}
Establishing effective energy performance benchmarking of a code under
intense development such as COSMO-ART is a challenging task because of
the  absolute necessity that  results must  be reproducible  within an
expected  variance for the  duration of  the Exa2Green  project. After
consultation  with  the  climate  community  to  properly  define  the
baseline,  it was  necessary to  find a  run-configuration  capable of
being recreated in all subsequent versions of the code.

Thus, we give here a brief  overview of the main features of the model
setup for  our benchmark's daily  runs.  Three-dimensional simulations
are performed over  Europe for April 13th 2010, which  is close to the
equinox and thus  brings benefits of having approximately  half day of
night  and half  day  of  sun exposure,  therefore  ensuring a  proper
activation of the chemistry cycle. We consider daily 24-hour forecasts
without  any  previous spin-up  simulations.   The calculation  domain
corresponds to  the CORDEX-EU-44  domain and is  covered by a  grid of
$222\times   216$    points   with   a    horizontal   resolution   of
$0.22\,^{\circ}$,  i.e.  50  km in  both directions,  and  40 vertical
layers.   Boundary  and initial  conditions,  emmissions and  external
parameters  were obtained by  the INT2LM  pre-processing interpolation
tool, which interpolate  data from a coarse-grid driving  model to the
rotated    latitude-longitude   grid    of   the    COSMO-Model,   and
INT2LM\_trcr\_ART,  which  interpolates  aerosol  or  gaseous  species
initial and boundary conditions  and consists mostly of the definition
of a large number of  tracers.  The meteorological initial and bounday
conditions are  obtained by  the the ECMWF  global spectral  model IFS
with an update  frequency of 3h.  Boundary data  for gas-phase species
are taken from IFS-MOZART output at 6h temporal resolution.  The model
setup incorporates  34 2-d and 45  3-d fields to be  written out every
hour and doesn't include data assimilation methods.
